First Attempt at a Comparison Matrix

### 2014-08-15 test-compare-codes.Rmd
Add labels to k-means plot

And now for k-means with a plot that I kind of get. Obviously this would make more sense with names on the plot.

```{r}
cluster <- kmeans(comparison_of_all_codes, centers = 5)
library(cluster)
clusplot(comparison_of_all_codes, cluster$cluster)
```

>>>>

And now for k-means with a plot that I kind of get.

```{r}
cluster <- kmeans(comparison_of_all_codes, centers = 5)
library(cluster)
clusplot(comparison_of_all_codes, cluster$cluster, labels = 2)
```
